
In this project, we performed an in-depth study of a two-dimensional discrete-time dynamical system given by two logistic maps. The aim was to investigate how the long-term behaviour of the system changes for different parameter values, using fixed points, periodic points, phase portraits and a bifurcation diagram. 

We have presented different developments of the system depending on the initial parameters. For smaller parameter values, trajectories may converge to a single attracting fixed point.
The theoretical fixed points were calculated and match the later obtained results with the exception of the symmetric case $r_1=r_2=3.1$, where $x=y=1-\frac{1}{3.1}=0.67741935$ theoretically exists. However, for these values of $r_1$ and $r_2$ this value is not observed in the numerical simulations as it is not attractive.
Instead, the system converges to a stable period-2 orbit, from what we can conclude that the existence of a fixed point alone is not enough to describe the 
observed long-term behaviour. It is therefore clear that the fixed point's stability is essential to describe the behaviour of the system. 

The symmetry between the two populations is broken when increasing $r_2$ while keeping $r_1=3.1$. In this case, the system still 
exhibits a period-2 behaviour which turns into an asymmetric orbit. For the tested parameter values, no genuine period-3 orbit was detected after checking the minimal period of the numerical solutions. For larger values of r such as $r_2=3.8$, the bifurcation cascade and 
the computation of periodic points both indicate a stable period-4 orbit.
With even greater values, such as $r_2=3.95$, the system no longer converges to a small number of points, but instead produces a point cloud, suggesting more complex and chaotic dynamics.

Overall, the different numerical approaches give a consistent picture.
The numerical calculations, phase portraits and bifurcation diagram all show a transition from simple attracting behaviour to period-doubling and then to increasingly complex dynamics.
This leads to the conclusion that deterministic systems can become highly complex, especially when two logistic maps are coupled, generating a behaviour that appears irregular or aperiodic despite being produced by deterministic rules.


