\section{Interpretation}

\input{texfiles/interpretation}
\newpage
\section{Conclusion}
\input{texfiles/conclusion}

\section{Use of LLM tools}
\subsection{Game of Life}
\paragraph{RLE prompt:}  Create an rle loader to import standard Game of Life patterns directly. The output was a
complete functional script \texttt{RLE.py} that parses strings like
\begin{quote}
\verb+24bo11b$22bobo11b$12b2o6b2...+
\end{quote}
, which encode binary patterns stored in a Wiki page.

\subsection{Game of Life}
\paragraph{Text Files prompt:}  Generate three text files containing the initial live-cell coordinates for an AND gate, an OR gate, and a NOT gate. The files should be called \texttt{AND.txt}, \texttt{OR.txt}, and \texttt{NOT.txt}. Each file should contain one live cell per line, written in the format \texttt{(x,y)}.

This was used to generate possible text files, so one can try running them with the code.




\subsection{Neuron Cellular Automaton}
The code in \verb+neuron.py+ is based on \verb+gameOfLifeInteractiveToric.py+ from the lecture. We used ChatGPT to modify the code. The prompt was 
"I would like to change the rules of the game. I need to have three different states for each cell now and new rules, how can I implement this?" and additionally added the 
original code. This returned good instructions on where the code needs modification. Additionally, we looked up the documentation of the functions used by ChatGPT and made 
some modifications to its suggestions.  

\newpage
\section*{Files submitted}
The following files have been submitted with this report: \\
\begin{enumerate}
  \item \verb+GameOfLife.py+
  \item \verb+GameOfLifeDebug.py+
  \item \verb+GoLogic.py+
  \item \verb+pattern_processing.py+
  \item \verb+RLE.py+
  \item \verb+NOT.txt+
  \item \verb+AND.txt+
  \item \verb+OR.txt+
\end{enumerate}


