\subsection{Methods}
In general, the code was inspired by having a look at the interactive version that Jordi shared but was rewritten from the ground up to keep the complexity reduced for the actual task at hand.
For representing the current state I chose to use a two-dimensional \texttt{numpy} array with integer values.
The application of the von Neumann neighbourhood is done by four wrapping shifts in the two cardinal directions, for each once with a positive and once with a negative shift of one.
The four shifted grids are assembled into a three-dimensional array to enable array operations on the entire neighbourhood at once.
For each cell that is non-zero the value is incremented by one before applying the modulo operator to keep the values in the proper range.
By the rules any ready cell is excited by at least one neighbour being in an excited state.
This can be checked by testing each value if it is larger than zero but less than or equal to the excitation parameter.
The any operation can be reduced over the third or stacking dimension.
Now all cells that were previously ready and have any excited neighbour are set to the value one.
For repeatedly stepping the model, the result of one step is used as the input to the next step.
If at any point all cells are zero, the event loop is exited because the will be no further changes with the progression of time.
Saving to and loading from file is done in a format that is similar to the format used for task 1 in the instructions.
Each line consists of a tuple with three values, first the two coordinates as for indexing a \texttt{numpy} array and last the value of the cell at that coordinate.
When loading the grid is initialized to be all zeros and overwrites all cells that are specified in the input.
Drawing to a grid is done by using \texttt{matplotlib}'s \texttt{imshow} function and a colour map.
Instead of reading from a configuration file the starting state can also be randomly generated.
In that case \SI{20}{\percent} of cells are set to random values in the interval 1 to $N$ where $N$ is the number of total states available for each cell.

For the aim to find the (eventual) periodicity of an initial configuration, the configuration is first read or an initial state generated.
Afterwards, the initial state is saved to a list.
Then, for each iteration we continue the automaton one step before checking if this new state is in this list.
If it is, then we found a periodic state because the exact same state has occurred before.
We exit the loop and optionally save the final state to a configuration file or an image and all members of the periodic orbit to individual images.
If it is not in the list, we add the state to the list of seen states.
The transient time can be found by getting the index of the previously seen state in the list.
Any time steps before the recurrent state were transient while the time since the first occurrence is the period of the orbit.

\subsubsection{Running the Code}
The common functions for stepping the automaton, initializing a random grid, reading and writing configurations are in the file \texttt{ghca\_common.py}.
The code for the application fulfilling the requirements from the unnumbered list can be found in \texttt{ghca\_advance.py} and can be configured with the following command-line arguments:
\begin{itemize}
	\item \texttt{-s} Setting the size of the periodic grid
	\item \texttt{-n} Setting the number of steps before stopping
	\item \texttt{-e} Setting the number of excited states
	\item \texttt{-N} Setting the number of total states
	\item \texttt{--seed} Setting a random number seed for reproducibility of the random initialization
	\item \texttt{--show} Enables showing the current state of the grid in a \texttt{matplotlib} window
	\item \texttt{--delay} Setting the delay after each step before continuing the loop
	\item \texttt{-o} Setting the output file for writing the final state to a configuration file
	\item \texttt{--save-image} Setting the output file for an visual/image ersion of the final state
	\item the filename of the configuration file to read from as a positional argument
\end{itemize}
The code for determining the period can be found in the file \texttt{ghca\_periodic.py}.
The command line arguments are very similar with the following differences:
\begin{itemize}
	\item no option to set the number of steps, it will run until it found a periodic orbit
	\item no delay parameter, for slowly inspecting the progression use the other program
	\item \texttt{--sequence-dir} to set a directory into which all members of the periodic orbit will be written as PNG files which can be used to create an animation
\end{itemize}