\subsection{Game of Life Numerics}

\subsubsection{Computational domain}
The computational domain is represented as a two-dimensional rectangular lattice
$X \in \{0,1\}^{n\times n}$, where each entry corresponds to one cell of the automaton.
The state variable is stored as an 8-bit unsigned integer array, \texttt{np.uint8}, in order to
minimize memory overhead while preserving the binary structure of the model. In the simulations
reported here, we use a square grid with $n=400$.

\subsubsection{Time evolution}
The time evolution is implemented as a composition of a linear convolution operation and a pointwise
non-linear update. The discrete convolution is computed using \texttt{scipy.ndimage.convolve}. A fixed
$3\times 3$ kernel
\begin{equation}
K =
\begin{bmatrix}
    1 & 1 & 1\\
    1 & 0 & 1\\
    1 & 1 & 1
\end{bmatrix}
\end{equation}
is used to compute the Moore neighbourhood sum
\begin{equation}
N^{(t)} = K * X^{(t)}.
\end{equation}
The central entry of the kernel is zero, so the cell itself is excluded from the neighbour count.

The Game of Life update rule is then applied by vectorized logical operations:
\begin{equation}
X^{(t+1)}
=
\mathbb{1}\!\left(N^{(t)} = 3\right)
\vee
\left[
X^{(t)} \wedge \mathbb{1}\!\left(N^{(t)} = 2\right)
\right].
\end{equation}
Thus, a dead cell becomes alive if it has exactly three live neighbours, while a live cell survives if
it has two or three live neighbours. The resulting Boolean array is cast back to \texttt{np.uint8}.

The update function allows both zero-padding boundaries, implemented with
\texttt{mode="constant"}, and periodic boundaries, implemented with \texttt{mode="wrap"}. For the
logical-gate simulations, zero-padding boundaries are used, since the gates are placed away from the
domain boundary and the construction is intended to represent a finite portion of an otherwise empty
Game of Life plane.

\subsubsection{Initial conditions}
Initial conditions are constructed programmatically in \texttt{GoLogic.py}. The basic components are
the Gosper glider gun and the eater, both stored in Run Length Encoding (RLE). The RLE strings are
parsed into binary arrays using a custom parser and inserted into the computational domain at fixed
coordinate offsets. This makes the construction reproducible, since each component is always placed
at the same location for a given input condition.

The code also implements geometric transformations of these base components, including rotations and
left-right or up-down reflections. This allows the same gun and eater patterns to be reused in
different orientations. The helper functions \texttt{add\_pattern} and \texttt{transform\_pattern}
are used to insert and transform the components before simulation.

In addition to programmatic construction, the script includes a function
\texttt{load\_live\_cells(filename, n)}, which can read initial configurations from external text
files. These files contain one live cell per line in the format \texttt{(x,y)}. The file is converted
into an $n\times n$ binary array by setting \texttt{grid[y,x] = 1}. This was used to support the
required coordinate-list representation of the initial gate configurations.

\subsubsection{Logical gates}
The logical gates \texttt{AND}, \texttt{OR}, and \texttt{NOT} are realized through spatial
arrangements of glider guns and eaters. Signals are represented by streams of gliders emitted by
Gosper glider guns. Logical input values are encoded by modifying the initial configuration: an input
value of $1$ corresponds to allowing the relevant signal to propagate, while an input value of $0$
corresponds to placing an eater so that the corresponding signal is suppressed.

For the \texttt{AND} and \texttt{OR} gates, all four input combinations were simulated:
\[
(A,B) \in \{(0,0),(0,1),(1,0),(1,1)\}.
\]
For the \texttt{NOT} gate, the two possible input values were simulated:
\[
A \in \{0,1\}.
\]
The output was read visually from the designated output lane. The presence of a propagating glider
stream in this lane was interpreted as logical output $1$, while its absence was interpreted as
logical output $0$.

\subsubsection{Simulation procedure and visualization}
For each gate, the corresponding initial condition is created on a $400\times 400$ lattice and then
iterated for \texttt{nsteps = 1000} time steps. The automaton is advanced explicitly by repeated
application of the update function. For visualization, \texttt{matplotlib.pyplot.imshow} is used with
a binary colour map, so that live and dead cells are directly represented as black and white pixels.

To compare input cases systematically, the simulations for each gate were displayed in a single
window. The \texttt{AND} and \texttt{OR} gates were shown using a $2\times 2$ subplot layout, with one
panel for each input pair. The \texttt{NOT} gate was shown using a $1\times 2$ layout, with one panel
for each input value. Each panel was labelled with the corresponding input condition, and the figure
title displayed the current time step. The axes were restricted to the active region of the lattice
so that the glider interactions and output signal were easier to observe.

\subsubsection{Debugging and validation}
Since the Game of Life update rule is not invertible, reverse time stepping is not defined. Validation
therefore relied on forward simulations and direct inspection of the time evolution. The simulation
was run for each input condition, and the observed outputs were compared with the expected Boolean
truth tables of the corresponding gates. The time-step label in the visualization made it possible to
select representative snapshots showing the initial configuration, signal propagation, gate
interaction, and final output behaviour.
