\subsection{Theory - Greenberg-Hastings Cellular Automaton}

The Greenberg-Hastings Cellular Automaton (GHCA) is a model defined on an $n\times n$ square lattice with $N$ different states for each cell. The grid evolves according to the rules presented in the following definition.

\begin{definitionbox}[label=def:GHCArules]{GHCA rules \cite{Lecture}}
On the square lattice, each cell can inhabit a "resting" state, in which it remains until activation. The cell can undergo "excitement", which means it exits the resting state and starts evolving through the $e-1$ excited states available. The cell will then reach the "refractory" states, of which there are $N-e-1$. In total, there are $N$ states. Each cell interacts with itself and with other cells in its Neumann neighbourhood, which include the 4 closest, non-diagonal, neighbours. The cell evolves according to the following rules:
\begin{enumerate}
\item \textbf{Resting}: A cell finds itself in this state a time-step after being in the final refractory state.

State $N \rightarrow$ State $0$.
\item \textbf{Excitation}: If a resting cell has at least one neighbour in the excited state, it turns excited in the next step. If the cell already is in one of the excited states, it evolves into the next excited state in the next time-step.

State $0 \leq k < e \rightarrow$ State $0 < k+1 \leq e$.
\item \textbf{Refractory}: A cell changes to the initial refracted state one time-step after reaching the final excited state. It then continues to evolve into each subsequent refractory state for each time-step. If the cell is in the final refractory state, next time-step sees it return to the resting state.

State $e \leq k < N \rightarrow$ State $e < k+1 \leq N$.
\end{enumerate}
\end{definitionbox}

The GHCA can be described as the following set: $u^{(t)} = (0,1,\dots,e,e+1\dots,N)^{n\times n}$, where $u^{(t)}_{(i,j)}$ gives the state of the cell at position $(i,j)$ in the grid at time $t$. In the equality, the $0$ denotes the resting state, the $1, \dots , e$ denote the excited states and the $e+1, \dots, N$ denote the refractory states. It can also be viewed as a discrete dynamical system 

GHCA is a dynamical model, which can start from whichever initial state and evolve according to the rules in definition \ref{def:GHCArules}. The evolution is difficult to predict, which makes this a chaotic system. As each cell can inhabit $N$ possible states and there are $n^2$ cells in the grid, which in turn gives the cardinality of the set of all possible initial conditions to be $N^{n^{2}}$.

This model is useful for simulating diffusion of wave patterns in excitable media. This is defined as a medium which can inhabit three possible states, a "ready" state, an "excited" state, and a "refractory" state, which are the origin of the names given in the definition. Generally, the ready state is the medium's equilibrium state, where it can be perturbed by its neighbours. The excited state is a temporary state which requires an initial stimulation to initiate and is then carried throughout the medium. Finally the refractory states are states which do not respond to stimulus and require some time to return to the medium's equilibrium. A good example to understand this type of medium is a forest, where the excitation is a fire and the refractory state is burned, barren land, though this is not associated with the following computation in any way.
