\subsection{Game of Life and Logic Gates}\subsubsection{Game of Life as a discrete dynamical system}

Conway's Game of Life can be viewed as a discrete dynamical system on a rectangular lattice
$X^{(t)} \in \{0,1\}^{m \times n}$, where each entry $X_{ij}^{(t)}$ represents the state of the cell
at site $(i,j)$ at time $t$. The evolution of the system is determined by update rules that specify
the state of each cell at the next time step, $X_{ij}^{(t+1)}$.

\begin{definitionbox}[label=conwayrules]{Conway's rules \cite{GoLInteractiveCode}}
\begin{enumerate}
\item \textbf{Survival}: a live cell stays alive if it has 2 or 3 live neighbors.
\item \textbf{Birth}: a dead cell becomes alive if it has exactly 3 live neighbors.
\item \textbf{Death by isolation}: a live cell dies if it has fewer than 2 live neighbors.
\item \textbf{Death by overcrowding}: a live cell dies if it has more than 3 live neighbors.
\item \textbf{Neighborhood}: the neighbors of a cell are the 8 surrounding cells.
\end{enumerate}
\end{definitionbox}

Let $N_{ij}^{(t)}$ denote the degree of node $X_{ij}^{(t)}$ at time $t$.
Since each cell has eight neighbors, the relevant directions are the cardinal and intercardinal
directions. Self-interaction is excluded, so the evolution of a cell depends only on its neighborhood.
The quantity $N_{ij}^{(t)}$ can be computed as

\begin{equation}
N_{ij}^{(t)} =
\sum_{p=-1}^1 \sum_{q=-1}^1 K_{p+2,q+2} X_{i+p,j+q}^{(t)},
\end{equation}

where $K$ is a $3 \times 3$ kernel. Equivalently,
\begin{equation}
N^{(t)} = K * X^{(t)},
\end{equation}
where $K * X^{(t)}$ denotes the convolution of the lattice $X^{(t)}$ with the kernel $K$.

The update rule can then be written as
\begin{equation}
X_{ij}^{(t+1)}
=
\begin{cases}
1, & \text{if } X_{ij}^{(t)} = 1 \text{ and } N_{ij}^{(t)} \in \{2,3\}, \\
1, & \text{if } X_{ij}^{(t)} = 0 \text{ and } N_{ij}^{(t)} = 3, \\
0, & \text{otherwise}.
\end{cases}
\end{equation}

In vectorized form, this becomes
\begin{equation}
X^{(t+1)} = \mathbb{1}\!\left(N^{(t)} = 3\right)
+ X^{(t)} \odot \mathbb{1}\!\left(N^{(t)} = 2\right),
\end{equation}
and we use dirichlet boundary conditons or zero padding to handle the adjacency of boundary nodes.
\newpage
\subsubsection{Logic gates in the Game of Life}
In classical computation, basic logic gates such as AND, OR, and NOT act on one or two input streams and produce a single output stream. For example,
\[
\begin{array}{ccc}
\begin{array}{@{}l@{}}
\texttt{01001010}\\
\texttt{10101010}\\
\hline
\texttt{00001010}
\end{array}
&
\begin{array}{@{}l@{}}
\texttt{01001010}\\
\texttt{10101010}\\
\hline
\texttt{11101010}
\end{array}
&
\begin{array}{@{}l@{}}
\texttt{01001010}\\
\hline
\texttt{10110101}
\end{array}
\\
\texttt{AND} & \texttt{OR} & \texttt{NOT}
\end{array}
\]
Such gates implement a local transformation of binary information.

In the Game of Life, which is a discrete dynamical system evolving on a lattice, one may view logic gates from a
different perspective: not as abstract Boolean operators, but as spatially embedded computational devices. The
initial state is a geometric configuration, and the update rule propagates that configuration through time (changes
its geometry from one to another). From this viewpoint, the construction of a logic gate becomes a problem of geometric
constraint and synchronization. The central question is which initial lattice configuration (i.e., which geometry) $X^{(0)}$
can, under Conway's rules, evolve so as to realize deterministic, time-dependent binary information processing in the form of
\texttt{AND}-, \texttt{OR}-, and \texttt{NOT}-gates?

First, we need to construct an initial geometry that evolves, under Conway's rules, into a space-time signal. For 
this we could use a train of \textit{gliders} that travels periodically and diagonally across the lattice
\cite{gliderwiki}. To get an arbitrary length of space-time signals we migh use \textit{guns} that generate 
gliders \cite{glidergunwiki}. The trajectories along which gliders evolve act as rigid wiring, thereby constraining
the direction of information flow. In the absence of any interference, the signal propagates persistently along these paths.
To obtain a richer computational structure, this simple stream of gliders (interpretable as a sequence of 1s) must be
complemented with the ability to represent absence (0s) as meaningful information. Furthermore, one requires mechanisms for
interaction between multiple input streams such that they can be combined to produce a third output stream, with the
resulting configurations remaining composable within larger constructions.

It is possible to realize \cite{golgatevideo} composable logic gates in the Game of Life by spatially arranging
glider guns, eaters,
and collision configurations such that controlled streams of gliders encode binary information.
In this setting, glider presence corresponds to logical \texttt{1}, while the absence of a glider
stream corresponds to \texttt{0}. By appropriately translating and positioning glider guns, and by
placing eaters as stabilizing and filtering structures, one can engineer deterministic collision patterns
that implement logical operations. Moreover, these constructions are required to be composable,
in the sense that the output of one gate can be routed as the input to another without loss of
computational fidelity.



\newpage
\subsubsection{Encoding of Inputs}


\begin{definitionbox}[label=signalencoding]{Encoding binary signals}
Signal generation is achieved using the Gosper glider gun, which produces a periodic sequence of gliders with fixed phase and spacing. Through geometric transformations (rotations and reflections), identical guns can be oriented to produce signals in any required intercardinal direction. Each gun occupies a finite region of the lattice (for the canonical gun, $36 \times 9$ cells), but its function is not the static occupancy of this region; rather, it continuously emits a sequence of mobile patterns that carry information across the lattice. Consequently, the encoding is fundamentally dynamic and cannot be reduced to a fixed memory footprint.
\newline

\begin{enumerate}
\item \textbf{Signal 1} \texttt{(TRUE)}: This is represented by the \textbf{prescence} of a \textbf{glider}. This
signal propagates dynamically across a spatial lane across the lattice in fixed intercardinal directions.
\item \textbf{Signal 0} \texttt{(FALSE)}: Defined as the \textbf{inexistence} of a \textbf{glider}.  Its realization
depends on observation point there are two basic cases
    \begin{itemize}
    \item \textbf{Blocking}: Physically \textit{obstructing} a Gosper gun.
    \item \textbf{Annihilation}: Using collision trajectories or \textit{eaters} to remove a glider from the stream
    \end{itemize}
\end{enumerate}
\end{definitionbox}
\begin{definitionbox}[label=sigintmech]{Signal Interaction Mechanics}
Logic is performed through the interaction of these signals. Because gliders are sensitive to
\textbf{synchronization}, the timing of these interactions is as important as their location.
\newline

\begin{enumerate}
\item \textbf{Glider-Glider Collision}: These collisions are different depending on their spatiotemporal initial
configuration.
    \begin{itemize}
    \item Requires: Antiparallel streams \&precies phase sync.
    \item Result: \textbf{Mutual Annihilation} (functioning as a switch) \textit{or} \textbf{Fragmentation}. It also
    induces a space-dependent signal delay.
    \end{itemize}
    \item \textbf{Glider-Eater Interaction}: These interactions are \("\)less\("\) sensitive to synchronization.
    \begin{itemize}
    \item Requires: Specific placement/orientation of the Eater.
    \item Result: \textbf{Glider Annihilation/Absorpbtion} or \textbf{fragmentation}.
    \end{itemize}
\end{enumerate}
\end{definitionbox}

\subsubsection{Reading outputs}
Reading the state of a logic gate in the Game of Life is a measurement of \textbf{spatial-temporal presence}. The output of a gate is not solely a boolean value, but a \textbf{vector}. Since the gliders only propagate along intercardinal diagonals (NE,NW,SE,SW), the observation window must be placed precisely in the "firing line" of the logic gate's exit path.

\paragraph{$4 \times 4$ Observation Window.} To detect a "1" signal (the presence of a glider), the observer must
define a static bounding box of 4×4 cells at a specific coordinate $(x,y)$ on the lattice. Because a glider is a
dynamic pattern that fits within $4\times 4$ area during its four-generation cycle.
\paragraph{Detection logic.} The output is considered to have the assigned \texttt{TRUE} value if the correct number of
live cells within the $4 \times 4$, and the distribution are characteristic of the glider.

\paragraph{Composition.} If a gate’s output needs to be routed to a different input, you must apply rotations or
reflections to the initial gun configuration to ensure the output vector aligns with the next gate's input requirements.

\paragraph{Synchorinization.} If the observation window is checked at generation $T$, but the glider arrives at $T+1$,
the \texttt{READ} might detect a partial pattern (fragmentation) or an empty box, resulting in a false \textbf{0}.
Strictly speaking, on could a priori calculate the Manhattan distance the glider travels to ensure the output is
sampled only when the signal has had enough generations to reach the observation box.

\subsubsection{Initial conditions for the different gates}
Initial conditions to AND:
Image
Then input is say SE, output is NW
